State of the Practice for Lattice Boltzmann Method Software

### 2022-03-06 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
reviewed abstract and section 6 - comparison of tool..

Software tools are used to support the development, verification, maintenance,
and evolution of software, software processes, and artifacts \citep[p.\
501]{GhezziEtAl2003}. Many tools are used by LBM software packages, as
summarized in Table~\ref{tbl_tools}.  The tools are subdivided into development
tools, dependencies, and project management tools.  In this section we answer
\rqref{RQ_CompareToolsProjMngmnt} by comparing aspects of the tool usage in LBM
to their utilization in the research software community in general.

@@

As mentioned in Section~\ref{SecSurfCorrectAndVerifiab}, continuous integration
is rarely used in LBM (3 of 24 packages or 12.5\%). This contrasts with the
frequency with which continuous integration is recommended in research software
development guidelines \citep{BrettEtAl2021, Brown2015, ThielEtAl2020,
Zadka2018, vanGompelEtAl2016}.  We could not find published data on the
frequency with which continuous integration is used in general research
software.  Our impression is that like LBM software, other research software
packages lag behind the recommended best practice of employing continuous
integration.

>>>>

Software tools are used to support the development, verification, maintenance,
and evolution of software, software processes, and artifacts \citep[p.\
501]{GhezziEtAl2003}. Many tools are used by LBM software packages, as
summarized in Table~\ref{tbl_tools}.  The tools are subdivided into development
tools, dependencies, and project management tools.  In this section we answer
\rqref{RQ_CompareToolsProjMngmnt} by comparing aspects of tool usage in LBM software packages to their utilization in the research software community in general.

@@

As mentioned in Section~\ref{SecSurfCorrectAndVerifiab}, continuous integration
is rarely used in LBM software (3 of 24 packages or 12.5\%). This contrasts with the frequency with which continuous integration is recommended in research software development guidelines \citep{BrettEtAl2021, Brown2015, ThielEtAl2020,
Zadka2018, vanGompelEtAl2016}.  We could not find published data on the
frequency with which continuous integration is used in general research
software.  Our impression is that like LBM software, other research software
packages lag behind the recommended best practice of employing continuous
integration.
